Response to Referees

### 2025-06-09 ms/ms.Rmd
address RC2.6: choice of downscaling method

The Geological Survey of Norway conducted and processed radiometric surveys over our study areas, as reported in Baranwal et al. [-@baranwalHelicopterborneMagneticElectromagnetic2013] and Ofstad [-@ofstadHelicopterborneMagneticRadiometric2015].
They provided us for each site four variables at 50 m resolution, which we downscaled to 10 m resolution by cubic spline resampling, using the *terra* package (v1.7) in R.

>>>>

The Geological Survey of Norway conducted and processed radiometric surveys over our study areas, as reported in Baranwal et al. [-@baranwalHelicopterborneMagneticElectromagnetic2013] and Ofstad [-@ofstadHelicopterborneMagneticRadiometric2015].
They provided us for each site four variables at 50 m resolution, which we downscaled to 10 m resolution by cubic spline resampling. 
Sensitivity analysis showed that Pearson correlations between cubic spline and bilinear resampling methods exceeded 0.99 for all radiometric variables, so we are confident that the choice of resampling method did not affect our results.

### 2025-06-09 ms/ms.tex
address RC2.6: choice of downscaling method

The Geological Survey of Norway conducted and processed radiometric surveys over our study areas, as reported in Baranwal et al. \citeyearpar{baranwalHelicopterborneMagneticElectromagnetic2013} and Ofstad \citeyearpar{ofstadHelicopterborneMagneticRadiometric2015}.
They provided us for each site four variables at 50 m resolution, which we downscaled to 10 m resolution by cubic spline resampling, using the \emph{terra} package (v1.7) in R.

>>>>

The Geological Survey of Norway conducted and processed radiometric surveys over our study areas, as reported in Baranwal et al. \citeyearpar{baranwalHelicopterborneMagneticElectromagnetic2013} and Ofstad \citeyearpar{ofstadHelicopterborneMagneticRadiometric2015}.
They provided us for each site four variables at 50 m resolution, which we downscaled to 10 m resolution by cubic spline resampling.
Sensitivity analysis showed that Pearson correlations between cubic spline and bilinear resampling methods exceeded 0.99 for all radiometric variables, so we are confident that the choice of resampling method did not affect our results.

### 2025-06-09 ms/submission/AuthorComments-egusphere-2025-1046.qmd
address RC2.6: choice of downscaling method

>>>>

We appreciate this attention to the potential impact of radiometric resampling methodology on our results. To address this concern, we added to our code a sensitivity analysis comparing cubic spline and bilinear resampling methods for downscaling the 50 m radiometric data. Using field measurement locations from both study sites, we extracted radiometric values resampled by both methods and calculated correlations for each radiometric variable (K, Th, U, TC). The correlations between cubic spline and bilinear resampling methods were very high, with the lowest correlation being 0.995. This near-perfect correlation demonstrates that the choice of resampling method has negligible impact on the spatial representation of radiometric variability at our target resolution.

The consistently high correlations across all radiometric variables indicate that our conclusions about radiometric predictive performance would remain unchanged regardless of resampling method. Since we now mention this fact in the _Materials and methods_, we do not raise this point specifically in the _Discussion_ -- in the interest of brevity.

They provided us for each site four variables at 50 m resolution, which we downscaled to 10 m resolution by cubic spline resampling[, using the *terra* package (v1.7) in R]{.deleted}. 
[Sensitivity analysis showed that Pearson correlations between cubic spline and bilinear resampling methods exceeded 0.99 for all radiometric variables, so we are confident that the choice of resampling method did not affect our results.]{.added}
:::
